\textbf{Characterizing Errors and Uncertainties in NEMD Simulations of Phonon Transport}

### 2018-04-12 Slides/r1/md_si.tex
..

\myitem Widely used to study thermal (phonon) transport in 
{\color{pigment}non-metallic} systems (C,Si,Ge).
\vspace{2mm}
\myitem System subjected to a temperature gradient using thermostats.
\vspace{2mm}
\myitem {\color{pigment}Steady-state} thermal energy exchange between
the thermostats is used in Fourier's law to estimate bulk thermal
conductivity~($\kappa$). \vspace{2mm}
\myitem Estimates are {\color{pigment}uncertain} and severely
{\color{pigment}under-predicted}.
\begin{itemize}
  \item Simulation length-scales $\ll$ phonon mean free path. \vspace{1mm}
  \item Thermostats reduce correlation b/w vibration modes.
\end{itemize}

@@

    \node{Non-Equlibrium Molecular Dynamics}
   child [concept color=blue!30]{ node {Noise}
        child { node {Experiment Data}}
        child { node {MD Simulation}}
    }
    child [concept color=yellow!30]{ node {Model Inadequacy}
    child { node {Upscaling}}
        child { node {Missing Physics}}
    }
    child [concept color=green!30]{ node {Inter-atomic Potential}
        child { node {Potential Selection}}
        child { node {Parameter Values}}
         }
    child [concept color=red!30]{ node {Simulation Set-up}
        child { node {System Size}}
        child { node {Heat flux/Thermal gradient}}
        child { node {Duration}}
    };

@@

\begin{itemize}
\myitem Bulk thermal conductivity is size-dependent.
\vspace{2mm}
\myitem Variability in applied thermal gradient~(Kapitza~effect).
\vspace{2mm}
\myitem Choice of the inter-atomic potential.
\vspace{2mm}
\myitem Nominal estimates of the potential parameters.

\begin{center}
\begin{figure}[htbp]
\vspace{-3mm}
  \includegraphics[width=0.9\textwidth]{./Figures/cond_size}
  \\ \vspace{2mm}
  \includegraphics[width=0.9\textwidth]{./Figures/temp_plot}
\end{figure}
\end{center}

@@

\myitem Quantify discrepancy in $\kappa$ between predictions and data.
\begin{itemize}
\item Construct a response surface for $\kappa(s,\frac{d\theta}{dx})$.
\end{itemize}
\vspace{2mm}
\myitem Perform sensitivity analysis of the potential parameters.
\begin{itemize}
\item Estimate derivative-based sensitivity measures~(DGSM).
\end{itemize}
\vspace{2mm}
\myitem Construct a reduced order surrogate for $\kappa$ using sparse
NEMD predictions.
\begin{itemize}
\item Use the surrogate for forward propagation of uncertainty, and global
sensitivity analysis. 
\end{itemize}
\vspace{2mm}
\myitem Calibrate the \textit{important} parameters in a Bayesian setting.

@@

\begin{center}
{\color{green}NVT} \hspace{5mm} $\rightarrow$ \hspace{5mm} {\color{cyan}NVE} \hspace{5mm}
$\rightarrow$ \hspace{5mm} {\color{magenta}NVE}
\\ \vspace{1mm}
\tiny \hspace{-5mm}[Eqilibrate system to 300 K] \hspace{1mm} [Equilibrate thermostats] \hspace{4mm}
 [Generate Data]
\\ \vspace{1mm}

@@

@@

\begin{center}
{\color{gray}NPT} \hspace{5mm} $\rightarrow$ \hspace{5mm} {\color{green}NVT} \hspace{5mm} $\rightarrow$ \hspace{5mm} 
{\color{cyan}NVE} \hspace{5mm}
$\rightarrow$ \hspace{5mm} {\color{magenta}NVE}
\\ \vspace{1mm}
\tiny [Relax system length] \hspace{1mm}[Eqilibrate system to 300 K] \hspace{1mm} [Equilibrate thermostats] \hspace{4mm}
 [Generate Data]
\\ \vspace{1mm}

@@

\begin{center}
\scriptsize
\begin{tcolorbox}[width=0.7\textwidth,colback=DeepSkyBlue!20,notitle,colframe=DeepSkyBlue!20,colupper=DeepSkyBlue4]
\vspace{-2mm}
\be
\mathcal{P}(\bm{X}\vert \bm{Y}) \propto \mathcal{P}(\bm{Y}\vert\bm{X})\mathcal{P}(\bm{X})
\nonumber
\ee
\end{tcolorbox}
\vspace{1mm}
\tiny{$\bm{X}:\{\alpha,\gamma\}$}
\end{center}

@@

\myitem Likelihood, $\mathcal{P}(\bm{Y}\vert\bm{X})$:
\begin{center}
\scriptsize
\begin{tcolorbox}[width=1.1\textwidth,colback=DeepSkyBlue!20,notitle,colframe=DeepSkyBlue!20,colupper=DeepSkyBlue4]
\vspace{-3mm}
\be
\mathcal{P}(\bm{Y}\vert\bm{X}) = \frac{1}{\sqrt{2\pi\sigma^2}}\exp\left[-\frac{(\kappa_{\tiny{\mbox{E}}} - 
\kappa_{\tiny{\mbox{MD}}})^2}{2\sigma^2}\right]
\nonumber
\ee
\end{tcolorbox}
\end{center}

@@

>>>>

\myitem Widely used to study thermal (phonon) transport in 
{\color{pigment}non-metallic} systems (C,Si,Ge).
\pause
\vspace{2mm}
\myitem System subjected to a temperature gradient using thermostats.
\pause
\vspace{2mm}
\myitem {\color{pigment}Steady-state} thermal energy exchange between
the thermostats is used in Fourier's law to estimate bulk thermal
conductivity~($\kappa$). 
\pause
\vspace{2mm}
\myitem Estimates are {\color{pigment}uncertain} and severely
{\color{pigment}under-predicted}.
\begin{itemize}
  \item Simulation length-scales $\ll$ phonon mean free path. \vspace{1mm}
  \item Thermostats reduce correlation b/w vibration modes.
\end{itemize}

@@

    \node{Non-Equilibrium Molecular Dynamics}
   child [concept color=blue!30]{ node {Noise}
        child { node {Experiment Data}}
        child { node {MD Simulation}}
    }
    child [concept color=yellow!30]{ node {Model Inadequacy}
    child { node {Upscaling}}
        child { node {Missing Physics}}
    }
    child [concept color=green!30]{ node {Inter-atomic Potential}
        child { node {Potential Selection}}
        child { node {Parameter Values}}
         }
    child [concept color=red!30]{ node {Simulation Set-up}
        child { node {System Size}}
        child { node {Heat flux/Thermal gradient}}
        child { node {Duration}}
    };

@@

\begin{center}
\begin{figure}[htbp]
  \includegraphics[width=0.9\textwidth]{./Figures/cond_size}
\end{figure}
\end{center}

\end{column}
\hspace{-15mm}
\begin{column}{0.5\textwidth}

\begin{center}
\begin{figure}[htbp]
  \includegraphics[width=0.9\textwidth]{./Figures/temp_plot}
\end{figure}
\end{center}

@@

\myitem Quantify discrepancy in $\kappa$ between predictions and data.
\begin{itemize}
\item Construct a response surface for $\kappa(s,\frac{d\theta}{dz})$.
\end{itemize}
\pause
\vspace{2mm}
\myitem Perform sensitivity analysis of the potential parameters.
\begin{itemize}
\item Estimate derivative-based global sensitivity measures~(DGSM).
\end{itemize}
\pause
\vspace{2mm}
\myitem Construct a reduced order surrogate for $\kappa$ using sparse
NEMD predictions.
\begin{itemize}
\item Use the surrogate for forward propagation of uncertainty, and global
sensitivity analysis. 
\end{itemize}
\pause
\vspace{2mm}
\myitem Calibrate the \textit{important} parameters in a Bayesian setting.

@@

\begin{center}
{\color{green}NVT} \hspace{5mm} $\rightarrow$ \hspace{5mm} {\color{cyan}NVE} \hspace{5mm}
$\rightarrow$ \hspace{5mm} {\color{magenta}NVE}
\\ \vspace{1mm}
\tiny \hspace{-5mm}[Equilibrate system to 300 K] \hspace{1mm} [Equilibrate thermostats] \hspace{4mm}
 [Generate Data]
\\ \vspace{1mm}

@@

\scriptsize
\vspace{10mm}
\tikz[overlay, remember picture] \node at (2.9,1) {
\begin{tcolorbox}[width=0.34\textwidth,colback=DeepSkyBlue4,notitle,colframe=DeepSkyBlue4,colupper=white]
\textsc{Functional Form}
\end{tcolorbox}
};
\tikz[overlay, remember picture] \node at (5.3,-0.16) {
\begin{tcolorbox}[width=0.8\textwidth,colback=DeepSkyBlue!20,notitle,colframe=DeepSkyBlue!20,colupper=DeepSkyBlue4]
\vspace{-2mm}
\be
\Phi(1,\ldots,N) = \sum\limits_{i,j(i<j)}v_{ij}^{(2)}(A,B,p,q,\alpha)\hspace{1mm}+\sum\limits_{i,j,k(i<j<k)}v_{ij}^{(3)}(\lambda,\gamma)\nonumber
\ee
\end{tcolorbox}
};
\pause
\normalsize

@@

\begin{center}
{\color{gray}NPT} \hspace{5mm} $\rightarrow$ \hspace{5mm} {\color{green}NVT} \hspace{5mm} $\rightarrow$ \hspace{5mm} 
{\color{cyan}NVE} \hspace{5mm}
$\rightarrow$ \hspace{5mm} {\color{magenta}NVE}
\\ \vspace{1mm}
\tiny [Relax system length] \hspace{1mm}[Equilibrate system to 300 K] \hspace{1mm} [Equilibrate thermostats] \hspace{4mm}
 [Generate Data]
\\ \vspace{1mm}

@@

\begin{center}
\scriptsize
\begin{tcolorbox}[width=0.7\textwidth,colback=DeepSkyBlue!20,notitle,colframe=DeepSkyBlue!20,colupper=DeepSkyBlue4]
\vspace{-3mm}
\be
\mathcal{P}(\bm{X}\vert \bm{Y}) \propto \mathcal{P}(\bm{Y}\vert\bm{X})\mathcal{P}(\bm{X})
\nonumber
\ee
\end{tcolorbox}
\vspace{1mm}
\tiny{$\bm{X}:\{\alpha,\gamma\}$}
\end{center}

@@

\myitem Likelihood, $\mathcal{P}(\bm{Y}\vert\bm{X})$:
\begin{center}
\scriptsize
\begin{tcolorbox}[width=1.1\textwidth,colback=DeepSkyBlue!20,notitle,colframe=DeepSkyBlue!20,colupper=DeepSkyBlue4]
\vspace{-4mm}
\be
\mathcal{P}(\bm{Y}\vert\bm{X}) = \frac{1}{\sqrt{2\pi\sigma^2}}\exp\left[-\frac{(\kappa_{\tiny{\mbox{E}}} - 
\kappa_{\tiny{\mbox{MD}}})^2}{2\sigma^2}\right]
\nonumber
\ee
\end{tcolorbox}
\end{center}

@@

\myitem Discrepancy between NEMD predictions and experiments is captured using a response surface. 
\pause
\vspace{2mm}
\myitem The impact of variability in applied thermal gradient seems negligible at least in the considered interval. 
\pause
\vspace{2mm}
\myitem Sensitivity analysis using DGSM could help mitigate computational costs.  
\pause
\vspace{2mm}
\myitem NEMD predictions are largely sensitivity towards $\alpha$ and $\gamma$.
\pause
\vspace{2mm}
\myitem Calibration should be performed in a Bayesian setting to account for all possible errors and uncertainties.  
\pause
\vspace{2mm}
\myitem Strategies presented can be easily extended to other systems and potentials.
